Using Scipion for Stream Image Processing at EM Facilities

### 2018-03-23 3.workflow_diamond.tex
before class
go home

\subsection{The eBIC facility at Diamond Light Source}

@@

Diamond has thousands of users every year, both academic and commercial, and it is vital that their data is kept secure and confidential. A user management system has been developed which allocates each user with a unique federal identity (IDs), and associates those user IDs with the experiments in which they partake in. Visits are structured such that all raw and processed data collected during an experiment are kept in one directory, and only the associated visitors have read and write permissions in that directory. Users may access their data through ISPyB \citep{ispb2011},  a Laboratory Information Management System (LIMS) combining sample tracking and experiment reporting  %The link between the user and their visits enables data management such as archiving data to a long-term tape storage system, or the Laboratory Information Management System ISPyB (REF. Delageniere et al Bioinformatics 2011). In contrast to the CNB setup, Diamond has integrated the microscopes in much the same fashion to that of the beamlines at the facility, as is shown in figure X

@@

>>>>

\subsection{Case 3: Scipion at eBIC facility at Diamond Light Source}

@@

Diamond has thousands of users every year, both academic and commercial, and it is vital that their data is kept secure and confidential. A user management system has been developed which allocates each user with a unique federal identity (IDs), and associates those user IDs with the experiments in which they partake in. Visits are structured such that all raw and processed data collected during an experiment are kept in one directory, and only the associated visitors have read and write permissions in that directory. Users may access their data through ISPyB \citep{ispb2011},  a Laboratory Information Management System (LIMS) combining sample tracking and experiment reporting  %The link between the user and their visits enables data management such as archiving data to a long-term tape storage system, or the Laboratory Information Management System ISPyB (REF. Delageniere et al Bioinformatics 2011). In contrast to the CNB setup, Diamond has integrated the microscopes in much the same fashion to that of the beamlines at the facility, as is shown in figure X
\subsubsection{Network Setup and IT Infrastructure}

@@

\subsubsection{Additional Software Developments: }

\subsection{Additional Sotware Developement: ISyB monitor}

0) headless <-- no GUI
1) Problem: access file system: very spensive using glob
2) Modify import movies so it can start  sever that waits until "something" tells it that there is a new file. [quien reporta activeQ como]
3) import though webservice << rama de diamond. pull request
[** quien crea el sistema de directorios, create project]
4) Wizard that creates normalized enviroment? Scipion workflow customiser. -> template scipion
5) IspyB monitor -> connect to IspyB.(thumbnail-mic and ctf, defocus, resolution)
[headless version]
urls: where is this in scipion (given that there is no SNRF and Diamond)

where is scipion monitor customizer

>>> que desencadena el proceso?

### 2018-03-23 3.workflow_scilifelab.tex
go home

The facilities can be accessed by Swedish researchers through 
a peer-reviewed process. Applications can be submitted through an application portal (\url{https://cryoem.scilifelab.se/}). % and will be evaluated once every three months based on their scientific merit and technical feasibility by a national Project Evaluation Committee. %On the other side, some time of the facility is reserved for internal research groups at Stockholm University. 
Internally, a online booking system centralize the reservations of the microscopes and other instruments [**ROB-JM name of the booking system and reference???].

At the beginning of 2016, the Cryo-EM facility at SciLifeLab became one of the early adopters of \scipion for on the fly data processing. Before, there were some home-made scripts to perform motion correction (with motioncorr) and CTF estimation (with Gctf) but the microscope operators recognized the importance of a more general framework. In particular, they were interested in the possibility of modify easily the processing workflow as well as provide users and staff with  graphical tools for data analysis and quick feedback regarding the data collection. Initially, the same setup script used at CNB was adopted, but it did not fully satisfy the facility requirements and a new one has been developed. In the following sections we will briefly describe the computational infrastructure at the SciLifeLab node [** The one in  Stockholm?] and the implementation of a Session Wizard to automate the initial setup while fetching information from other sources external to \scipion.

@@

\subsubsection{Session Wizard}
In order to interface \scipion with the microscope infrastructure an upgraded version of the original script developed at the CNB was used. Unfortunately, it was difficult to reuse the existing code due to a different folder structure and, more important, a different logic about users and microscopes management. To address the new set of requirements, a new wizard is under development at SciLifeLab. For this new wizard, a basic data model was designed representing the current processing and data organization at SciLifeLab. The model is composed by the following entities:

\begin{itemize}
\setlength\itemsep{0em}
 \item \textit{User}: represents all persons that can book microscope time or are registered in the Application Portal 
 related to national projects.
 \item \textit{Reservation}:  is a resource (e.g, Krios, Talos, Vitrobot, etc) booking for a given period of time.
 \item \textit{Order}:  is a given national project with an unique identifier in the Application Portal
 \item \textit{Project}:  can be a either a national project (related to a given Order) or an internal project.
 \item \textit{Session}:  stores information about the usage of the micrograph for a given day.
\end{itemize}

>>>>

The facilities can be accessed by Swedish researchers through 
a peer-reviewed process. Applications can be submitted through an application portal (\url{https://cryoem.scilifelab.se/}). % and will be evaluated once every three months based on their scientific merit and technical feasibility by a national Project Evaluation Committee. %On the other side, some time of the facility is reserved for internal research groups at Stockholm University. 
Internally, a online booking system called \emph{Booked Scheduler} centralizes the reservations of the microscopes and other instruments.

At the beginning of 2016, the Cryo-EM facility at SciLifeLab became one of the early adopters of \scipion for on the fly data processing. Before, there were some home-made scripts to perform motion correction (with motioncorr) and CTF estimation (with Gctf) but the microscope operators recognized the importance of a more general framework. In particular, they were interested in the possibility of modify easily the processing workflow as well as provide users and staff with  graphical tools for data analysis and quick feedback regarding the data collection. Initially, the same setup script used at CNB was adopted, but it did not fully satisfy the facility requirements and a new one has been developed. In the following sections we will briefly describe the computational infrastructure at the SciLifeLab node at Stockholm and the implementation of a Session Wizard to automate the initial setup while fetching information from other sources external to \scipion. 
[** thalos falcon III, titan k2 and falcon III]

@@

\subsubsection{Additional Software Developments: \emph{Session Wizard}}
In order to interface \scipion with the microscope infrastructure an upgraded version of the original script developed at the CNB was used. Unfortunately, it was difficult to reuse the existing code due to a different folder structure and, more important, a different logic about users and microscopes management. To address the new set of requirements, a new wizard is under development at SciLifeLab. For this new wizard, a basic data model was designed representing the current processing and data organization at SciLifeLab. The model is composed by the following entities:

[** quitar modelo de datos]
\begin{itemize}
\setlength\itemsep{0em}
 \item \textit{User}: represents all persons that can book microscope time or are registered in the Application Portal 
 related to national projects.
 \item \textit{Reservation}:  is a resource (e.g, Krios, Talos, Vitrobot, etc) booking for a given period of time.
 \item \textit{Order}:  is a given national project with an unique identifier in the Application Portal
 \item \textit{Project}:  can be a either a national project (related to a given Order) or an internal project.
 \item \textit{Session}:  stores information about the usage of the micrograph for a given day.
\end{itemize}

### 2018-03-23 6.acknowledgments.tex
go home

The authors would like to acknowledge economical support from:
The Spanish Ministry of Economy and Competitiveness through Grants BIO2013-44647-R, BIO2016-76400-R(AEI/FEDER, UE) and AEI/FEDER BFU 2016 74868P, the Comunidad Aut\'{o}noma de Madrid through Grant: S2017/BMD-3817, European Union (EU) and Horizon 2020 through grant CORBEL (INFRADEV-1-2014-1, Proposal: 654248). This work used the EGI Infrastructure and is co-funded by the EGI-Engage project (Horizon 2020) under Grant number 654142. European Union (EU) and Horizon 2020 through grant West-Life (EINFRA-2015-1, Proposal: 675858) European Union (EU) and Horizon 2020 through grant Elixir - EXCELERATE (INFRADEV-3-2015, Proposal: 676559) European Union (EU) and Horizon 2020 through grant iNEXT (INFRAIA-1-2014-2015, Proposal: 653706). The authors acknowledge the support and the use of resources of Instruct, a Landmark ESFRI project.

>>>>

The authors would like to acknowledge economical support from:

The Spanish Ministry of Economy and Competitiveness through Grants BIO2013-44647-R, BIO2016-76400-R(AEI/FEDER, UE) and AEI/FEDER BFU 2016 74868P, the Comunidad Aut\'{o}noma de Madrid through Grant: S2017/BMD-3817, European Union (EU) and Horizon 2020 through grant CORBEL (INFRADEV-1-2014-1, Proposal: 654248). The ``Knut \& Alice Wallenberg Foundation'', and ``A Pilot Facility development grant from Science for Life Laboratory''.

This work used the EGI Infrastructure and is co-funded by the EGI-Engage project (Horizon 2020) under Grant number 654142. European Union (EU) and Horizon 2020 through grant West-Life (EINFRA-2015-1, Proposal: 675858) European Union (EU) and Horizon 2020 through grant Elixir - EXCELERATE (INFRADEV-3-2015, Proposal: 676559) European Union (EU) and Horizon 2020 through grant iNEXT (INFRAIA-1-2014-2015, Proposal: 653706). The authors acknowledge the support and the use of resources of Instruct, a Landmark ESFRI project. This work has used the Cryo-EM Swedish National Facility funded by the Knut and Alice Wallenberg, Family Erling Persson and Kempe Foundations, SciLifeLab, Stockholm University and Ume\aa\ University.

We acknowledge Diamond for access and support of the Cryo-EM facilities at the UK national electron bio-imaging centre (eBIC), funded by the Wellcome Trust, MRC and BBSRC.

### 2018-03-23 scipionbox.tex
before class
go home

%\usepackage{lineno}
\usepackage[update,prepend]{epstopdf}
%\linenumbers
\definecolor{lightgreen}{rgb}{0.75,0.75,0.0}
%\usepackage{caption}
%\usepackage{endfloat}
%\DeclareCaptionFormat{empty}{}
%\captionsetup{format=empty}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\footnotesize  \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\def\scipionbox{\textit{ScipionBox}\xspace}
\def\scipion{\textit{Scipion}\xspace}
\def\emadmin{\textit{EMAdmin}\xspace}
\newcommand{\protocol}[1]{\texttt{#1}}

@@

\begin{document}
\title{Using Scipion for Stream Image Processing at EM Facilities}
\author{XXXX$^{(a)}$,\\
        YYYY$^{(b)}$,\\
        }

@@

\lyxaddress{{\small \vspace{-0.5cm}$^{(a)}$Escuela Polit\'{e}cnica Superior, Universidad Aut\'{o}noma de Madrid, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(b)}$ Biocomputing Unit, National Center for Biotechnology (CSIC), C/ Darwin, 3, Campus Universidad Aut\'{o}noma, 28049 Cantoblanco, Madrid, Spain.}}

%This document provides a preliminary analysis of the data collected by the CTF Challenge (http://i2pc.cnb.csic.es/3dembenchmark/LoadHome.htm). Figures/tables/plots/etc are located at the document's end. 
\setcounter{figure}{2}%I do not know why but figure counter starts with -1
\textbf{Corresponding Author:} %Roberto Marabini, Ph= 34 91 5854510, email: roberto@cnb.csic.es\\
%Escuela Polit\'{e}cnica Superior\\
%Universidad Aut\'{o}noma de Madrid\\
%28049 Cantoblanco\\
%Madrid\\
%Spain

>>>>

%\usepackage{lineno}
\usepackage[update,prepend]{epstopdf}
%\linenumbers
\definecolor{lightgreen}{rgb}{0.75,0.75,0.0}
%\usepackage{caption}
%\usepackage{endfloat}
%\DeclareCaptionFormat{empty}{}
%\captionsetup{format=empty}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot[R]{\footnotesize  \thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\def\scipionbox{\textit{ScipionBox}\xspace}
\def\scipion{\textit{Scipion}\xspace}
\def\emadmin{\textit{EMAdmin}\xspace}
\def\epu{\textit{EPU}\xspace}
\newcommand{\protocol}[1]{\texttt{#1}}

@@

\begin{document}
\title{Using Scipion for Stream Image Processing at EM Facilities}
\author{Scipion Boys$^{(a)}$,\\
Jos\'e Miguel de la Rosa-Trev\'{i}n$^{(c)}$,\\
Marta Carroni$^{(c)}$,\\
Stefan Fleichman$^{(c)}$,\\
Erik Lindahl$^{(c,d)}$\\
Ashton AW$^{(e)}$,\\
Basham M$^{(e)}$,\\
Clare DK$^{(e)}$,\\
Savage K$^{(e)}$,\\
Siebert CA$^{(e)}$,\\
        }

@@

\lyxaddress{{\small \vspace{-0.5cm}$^{(a)}$Escuela Polit\'{e}cnica Superior, Universidad Aut\'{o}noma de Madrid, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(b)}$ Biocomputing Unit, National Center for Biotechnology (CSIC), C/ Darwin, 3, Campus Universidad Aut\'{o}noma, 28049 Cantoblanco, Madrid, Spain.}}
\lyxaddress{{\small$^{(c)}$ Department of Biochemistry and Biophysics, Science for Life Laboratory, Stockholm University, Stockholm, Sweden}} 
\lyxaddress{{\small$^{(d)}$ Swedish e-Science Research Center, KTH Royal Institute of Technology, Stockholm, Sweden}}
\lyxaddress{{\small$^{(e)}$ Diamond Light Source, Harwell Science and Innovation Campus, Didcot OX11 0DE, England}}
%This document provides a preliminary analysis of the data collected by the CTF Challenge (http://i2pc.cnb.csic.es/3dembenchmark/LoadHome.htm). Figures/tables/plots/etc are located at the document's end. 
\setcounter{figure}{2}%I do not know why but figure counter starts with -1
\textbf{Corresponding Author:} %Roberto Marabini, Ph= 34 91 5854510, email: roberto@cnb.csic.es\\
%Escuela Polit\'{e}cnica Superior\\
%Universidad Aut\'{o}noma de Madrid\\
%28049 Cantoblanco\\
%Madrid\\
%Spain
